Modeling the near-wake of a vertical-axis cross-flow turbine with 2-D and 3-D RANS

### 2016-09-25 reviews/reviewer3-response.md

>2. No the convergence study for 3d model in this paper.

This is true, we did not perform a true convergence study for the 3-D model. We
simply extrapolated the 2-D grid into three dimensions. While this may not be
ideal, this strategy may be useful to practitioners looking to perform similar
simulations, but do not have the computational resources to perform multiple
high fidelity 3-D simulations. The paper has been adjusted to clarify this
point.

>3. In Performance Prediction session, the author gives a figure(Fig.6 ) to show the comparison of 3d , 2d and experimental data. But fig.6 only gives the results for one case for different methods. The 2d method seems over-predict the Cp and Cd. more results of different cases should be given to verify this idea.

For this study we were mainly looking to model the near-wake at peak performance
(determined experimentally), rather than the entire performance envelope. The
performance predictions are therefore an indication of the loading on the
turbine and the level to which it imparts force onto the flow. Notes have been
added to the manuscript to clarify this point.

### 2016-09-25 paper.tex
Clarify that we were only looking at optimal TSR

We seek to validate 2-D and 3-D blade-resolved RANS models against the UNH-RVAT
mechanical power and near-wake measurements. If the blade loading and velocity
in the near-wake match well enough, the flow field can potentially be inspected
in greater detail, i.e., we may be able to make observations of quantities not
measured experimentally, e.g., pressure, and gain greater insight into where the
dominant flow structures originate. This will ultimately help develop and
evaluate low-order wake generator models for use in turbine array modeling. In
summary, the questions we hope to answer here are:

@@

Predictions for both the mean rotor power and drag coefficients are shown in
Figure~\ref{fig:br-cfd-perf-bar-chart}. In general, the 2-D CFD cases both
significantly overpredict turbine loading and therefore mechanical power output,
which is due to their increased blockage ratio, unresolved blade end effects,
and lack of blade support struts.

@@

    \caption{Power (left) and drag (right) coefficient predictions from
        experiments and each numerical model.}

>>>>

We sought to validate 2-D and 3-D blade-resolved RANS models against the
UNH-RVAT mechanical power and near-wake measurements taken at the experimentally
determined optimal tip speed ratio $\lambda_0 = 1.9$. If the blade loading and
velocity in the near-wake match well enough, the flow field can potentially be
inspected in greater detail, i.e., we may be able to make observations of
quantities not measured experimentally, e.g., pressure, and gain greater insight
into where the dominant flow structures originate. This will ultimately help
develop and evaluate low-order wake generator models for use in turbine array
modeling. In summary, the questions we hope to answer here are:

@@

Predictions for both the mean rotor power and drag coefficients at the optimal
tip speed ratio $\lambda_0 = 1.9$ are shown in
Figure~\ref{fig:br-cfd-perf-bar-chart}. In general, the 2-D CFD cases both
significantly overpredict turbine loading and therefore mechanical power output,
which is due to their increased blockage ratio, unresolved blade end effects,
and lack of blade support struts.

@@

    \caption{Power (left) and drag (right) coefficient predictions at $\lambda =
    1.9$, from experiments and each numerical model.}
